Databrary: Enabling sharing and reuse of research video

### 2015-01-30 jcdl-15/paper.tex
more tiny language tweaks

Our approach is to focus on video and audio recordings in particular research domains, and build appropriate structured and unstructured resources around this functional core.
By investigating how researchers studying human development and education organize their own data, we have identified a unifying set of principles for organizing contextual metadata.
This facilitates the capture, standardization, discovery, and understanding of data to enable reuse of recordings at an unprecedented scale.
We achieve this conformance through in-depth, investigative curation of previously collected datasets, and user interfaces allowing researchers to upload their own research data as they acquire it.
In the future, we hope to capture additional annotation data researchers already produce while analyzing recordings to further improve our discovery capabilities.

>>>>

Our approach is to focus on video and audio recordings in particular research domains, and build appropriate structured and unstructured resources around this functional core.
We designed the system by investigating how researchers studying human development and education organize their own data, deriving from those observations a unifying set of principles for organizing contextual metadata.
This facilitates the capture, standardization, discovery, and understanding of data to enable reuse of recordings at an unprecedented scale.
We achieve this conformance through in-depth, investigative curation of previously collected datasets, and user interfaces allowing researchers to upload their own research data as they acquire it.
In the future, we hope to capture additional annotation data researchers already produce while analyzing recordings to further improve our discovery capabilities.
